# Preprocess

Preprocess the `train` and `test` data in parallel.

```{r}
cl <- makeCluster(2)
registerDoParallel(cl)
```

Preprocessing steps

1. Remove highly correlated continuous predictors
2. Remove near-zero variance categorical predictors
3. Create dummy indicator variables for remaining categorical predictors
4. Remove dummy indicator variables corresponding to linear combinations

```{r}
L1 <- list(train, test)
L2 <- foreach (i = 1:length(L1)) %dopar% {
  library(magrittr)
  library(dplyr)
  library(caret)
  select(L1[[i]], -matches(paste(contHighCorr, collapse = "|"))) %>%
    select(-matches(paste(nearZero$rowname, collapse = "|"))) %>%
    names() %>%
    paste(collapse = " + ") %>%
    paste("~ ", .) %>%
    formula() %>%
    dummyVars(data = L1[[i]], sep = "_") %>%
    predict(newdata = L1[[i]]) %>%
    data.frame() %>%
    select(-matches(paste(catDummiesLinCom, collapse = "|")))
}
train <- L2[[1]]
test <- L2[[2]]
```

Stop the clusters.

```{r}
stopCluster(cl)
```

Check that the columns in `train` are the same as in `test`.
Show the columns that are not in both data sets.
*These are predictor values that are not in both data sets.*

```{r}
uncommon <-
  merge(data.frame(col = names(train), inTrain = TRUE),
        data.frame(col = names(test), inTest = TRUE),
        by = "col", all = TRUE) %>%
  filter((is.na(inTrain) | is.na(inTest)) & col != "loss")
uncommon
```

Remove these predictors from both data sets.

```{r}
train <- select(train, -matches(paste(uncommon$col, collapse = "|")))
test <- select(test, -matches(paste(uncommon$col, collapse = "|")))
dim(train)
dim(test)
```
